%%%
\subsection{Import}
\begin{lstlisting}
import pandas as pd
\end{lstlisting}

%%%
\subsection{Data Frames}
Data Frames are like numpy record arrays.

%
\subsubsection{add}
Use this method to add two data frames together
  \begin{itemize}
    \item use the {\color{red}{fill\_value=0}} argument to replace NaN with 0
  \end{itemize}

%
\subsubsection{columns}
List the column names
  \begin{itemize}

    \item access the column data by using attribute notation (handle.name) or
      dictionary notation (handle['name'])

    \item \color{red}{If the column name is more than one word you must use
      the dictionary notation}
  \end{itemize}

%
\subsubsection{cumsum}
Returns a cumulative sum for each column
  \begin{itemize}

    \item to return the cumulative sum for each row add the argument
      \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{columns.names}
\textit{list} Add column header names to displayed output

%
\subsubsection{corr}
Return the correlation of the data columns.

%
\subsubsection{describe}
Returns summary statistics for the data frame

%
\subsubsection{drop}
Remove an index (row or column)
  \begin{itemize}

    \item Example: remove row named "b"
\begin{lstlisting}
df = df.drop["b"]
\end{lstlisting}

    \item Example: remove columun named "b"
\begin{lstlisting}
df = df.drop["b", axis=1]
\end{lstlisting}

    \item Operation is not done in place.  To save the modified data frame
      assign it to a new handle.

    \item Add the argument \color{red}{axis=1} to drop a column
  \end{itemize}

%
\subsubsection{dropna}
Returns a dataframe with all rows containing any null values removed.
  \begin{itemize}

    \item By adding the argument {\color{red}{how='all'}} only the rows that
      contain all null removed.

    \item By adding the argument {\color{red}{axis=1}} the columns will be
      removed in lieu of the rows.

    \item By adding the argument {\color{red}{thresh}} equal to an integer n
      rows or columns with less than n items will be removed.
  \end{itemize}

%
\subsubsection{fillna}
Fills all the null values with the given value.
  \begin{itemize}

    \item If a {\color{red}{dictionary}} is passed to fillna it is possible
      to assign different fill values based on column.

    \item Argument {\color{red}{inplace=True}} will permanently alter the
      original dataframe.
  \end{itemize}

%
\subsubsection{head}
Returns the first n rows

%
\subsubsection{idxmin}
Returns the index of the each column maximum value
  \begin{itemize}

    \item to find index of the maximum values for each of the rows enter
      the argument \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{idxmin}
Returns the index of the each column minimum value
  \begin{itemize}

    \item to find index of the minimum values for each of the rows enter
      the argument \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{index.names}
\textit{list} Add index header names to the displayed output

%
\subsubsection{ix}
Returns the row data (handle.ix[3])
  \begin{itemize}

    \item \color{red}{if additional rows and columns are added using this
      command it will have the same effect as calling reindex.}
  \end{itemize}

%
\subsubsection{max}
Find the maximum value of each column
  \begin{itemize}

    \item to find the maximum value for the rows enter the argument
      \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{merge}
  \begin{itemize}
    \item combines two data frames common elements
  \end{itemize}

%
\subsubsection{min}
Find the minimum value of each column
  \begin{itemize}

    \item to find the minimum value for the rows enter the argument
      \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{pct\_change}
Returns the item by item percent change along the columns for each row.
  \begin{itemize}

    \item to view the percent change across the rows enter the argument
      \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{plot}
Uses matplotlib to plot the each column of the data frame.
  \begin{itemize}

    \item {\color{red}{make sure to import matplotlib before calling this
      method}}

    \item to see the graph call {\color{red}{plt.show()}}

    \item if using Jupyter notebooks call {\color{red}{\%matplotlib inline}}
  \end{itemize}

%
\subsubsection{reindex}
Allows rows or columns to be reindexed
  \begin{itemize}

    \item \color{red}{if no arguments are passed the rows will be reindexed,
      and if the columns argument is passed the columns will be reindexed.}
  \end{itemize}

%
\subsubsection{sum}
Returns the sum of the columns
  \begin{itemize}

    \item to sum the rows enter the argument \color{red}{axis=1}
  \end{itemize}

%
\subsubsection{swaplevel}
If multiple indices are used this method will swap their order
  \begin{itemize}

    \item to swap the columns indices add the argument {\color{red}{axis=1}}
  \end{itemize}

%
\subsubsection{tail}
Returns the last n rows

%%%
\subsection{Excel with Python}

%
\subsubsection{Required Installs}
\begin{lstlisting}
pip install xlrd
pip install openpyxl
\end{lstlisting}

%
\subsubsection{Open Excel File}
\begin{lstlisting}
xls_file = pd.ExcelFile('file_name.xlsx')
data_frame = xls_file.parse('Sheet1')
\end{lstlisting}


%%%
\subsection{io}

%
\subsubsection{data}
  \begin{itemize}

    \item \textbf{pd.io.data.get\_data\_yahoo()} may be used to get stock prices
      from yahoo finance
  \end{itemize}

%
\subsection{Multiple Indices}

%
\subsubsection{Series}
\begin{itemize}
  \item Assigning multiple indices to a Series will cause it to act like a
    DataFrame

  \item \textbf{unstack} Returns a DataFrame of the multi-index Series
\end{itemize}
\begin{lstlisting}
group = sorted([1, 2] * 3)
idx = ['a', 'b', 'c'] * 2
ser = pd.Series(np.random.randn, index=[group, idx])
df = ser.unstack()
\end{lstlisting}

%%%
\subsection{Read Files}
\begin{lstlisting}
df = pd.read_csv
\end{lstlisting}

%%%
\subsection{Read HTML}

%
\subsubsection{Dependencies}
\begin{itemize}

  \item Beautiful Soup

  \item html5lib
\end{itemize}
\begin{lstlisting}
pip install beautifulsoup4
pip install html5lib
\end{lstlisting}

%
\subsubsection{Import read\_html}
\begin{lstlisting}
from pandas import read_html
\end{lstlisting}

%
\subsubsection{Create List of Data Frames}
\begin{lstlisting}
url = 'string_address_here'
df_list = pd.io.html.read_html(url)
\end{lstlisting}

%%%
\subsection{Read From Clipboard}
This function will take anything on the system clipboard and attempt to convert
it into a DataFrame.
\begin{lstlisting}
pd.read_clipboard()
\end{lstlisting}

%%%
\subsection{Series}
This is a vector.

\subsubsection{drop}
Remove an index row
  \begin{itemize}

    \item Example row drop: ser.drop['b']

    \item Operation is not done in place.  To save the modified series
      assign it to a new handle.
  \end{itemize}

\subsubsection{dropna}
Removes all null values.

\subsubsection{isnull}
Returns boolean array based on null value.

\subsubsection{rank}
Return the value rank with respect to index.

\subsubsection{reindex}
Will assign a new index list to the series.
  \begin{itemize}

    \item \textbf{fill\textunderscore value} argument to insert a specific
      value for missing data.

    \item \textbf{method} allows functions to define the reindex
      \begin{itemize}

        \item \textbf{ffill} Forward Fill will propagate a known value for
          missing data until a new known value is found.  Then the new value
          is propagated for missing data until the next known value is found.

        \item \textbf{bfill} Backward Fill is the same as Forward Fill only
          the propagation goes backward.

        \item \textbf{nearest} Uses the nearest value to propagate unknown
          values.
      \end{itemize}
  \end{itemize}

\subsubsection{sort\_index}
Will sort the series based on index when no arguments are provided.

\subsubsection{sort\_values}
Will sort the series based on value when no arguments are provided.

\subsubsection{unique}
Returns the unique values of a series.

\subsubsection{value\_counts}
Returns the number of times each values occurs in the series.

